Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-12 inc/appendix/script.tex
Added text to the appendix demonstrating the scripts.

@@

@@

>>>>

In this appendix, I want to introduce the Perl implementation of the extended AG model, called \verb!Physics::UEMColumn!.
This distribution has been released as open source software under the terms of the Artistic License (a derivative of the GNU General Public License), which allows for free use of the software.
The current state of development is available at \url{https://github.com/jberger/Physics-UEMColumn}, while official releases are available via the Comprehensive Perl Archive Network (CPAN) and its many tracker websites, see for example \url{https://metacpan.org/module/Physics::UEMColumn}.

The module is implemented as fully object-oriented Perl.
For ordinary differential equation solving, it employs a custom designed, closure-based interface to the GNU Scientific Library (GSL, \url{http://www.gnu.org/software/gsl/}), which uses a Runge-Kutta Prince-Dormand (8,9) step function (RK8PD), so that the numerical equation solving is both fast and accurate (see \url{https://metacpan.org/module/PerlGSL::DiffEq}).
I have also developed a system by which the object framework can use input units of the user's choosing for convenience (see \url{https://metacpan.org/module/MooseX::Types::NumUnit}).

To write a simulation script, the end-user need only define physical parameters of the system as instances of certain classes, and appropriately add them to the overall simulation object of class \verb!Physics::UEMColumn!.
In the following script, which produces \ref{fig:compound} (the compound element system), this occurs in lines 11-63.
The \verb!propagate! method call (line 65) then performs all of the simulations given the current state of the overall \verb!Physics::UEMColumn! object, which returns a two-dimensional Perl array of results.
The columns are, in this order: elapsed time $t$, pulse center position $z^{\prime}$, velocity of the pulse center $v_{\smallzero}$, $\sigma_{\smallT}$, $\sigma_{z}$, $\gamma_{\smallT}$, $\gamma_{z}$, $\eta_{\smallT}$, $\eta_{z}$.
In line 65 I immediately load the returned data into the Perl numerical library PDL (see \url{http://pdl.perl.org}), which is rather like MatLab.
Using this PDL object, I extract the pulse position (column 1, zero indexed), and the spatial variances (columns 3 and 4).
I then plot the the data in terms of the normalized width and length of the pulse.

@@

As a further example, I also include the script used to generate \ref{fig:spacecharge_noacc} and \ref{fig:spacecharge_acc}.
In this example, in lines 12-56 I define a function, which simulates the pulse dynamics for a given number of electrons with the option of having a realistic photocathode and acceleration region or an idealized pulse.
From there, I loop over a set of predefined number of charges per pulse, simulate each sequentially and extract the final pulse dimensions after a propagation distance of 15cm.
I write this data to a file to be plotted elsewhere.

@@

I present these examples to demonstrate the utility of the Perl implementation of the AG model; I hope it will be useful to other members of the UEM community.
Other examples may be seen in the source repository for this thesis, which is available at \url{https://github.com/jberger/Thesis}.

### 2013-04-12 inc/extension/implementation/implementation.tex
Added text to the appendix demonstrating the scripts.

A simulation script is composed of creating instances of the classes that represent the column, the pulse, electron-optical elements like magnetic lenses and RF cavities.
These objects act as containers for the information about the physical object that they represent.
Further they manage programmatic tasks related to those objects.
For example, electron-optical element objects manage the Gaussian region-of-influence (\ref{eq:reg_of_influence}) and calculate the force that their fields apply to the pulse.
This allows for clean, manageable and extensible code.

These objects are managed by a central ``simulation'' class (called \verb!Physics::UEMColumn!) which handles the time evolution of the system.
The source package contains an example script analogous to the optical Cooke triplet, containing a magnetic lens, RF cavity and another magnetic lens.
This script is included as Appendix \ref{sec:script}.

Many scripts which use \verb!Physics::UEMColumn! were need to generate data used in the writing of this thesis.
I have included most of them in the source repository which is available at \url{https://github.com/jberger/Thesis}.

Additionally, a development version of the bin model presented in Section \ref{sec:bin_model} is available at \url{https://github.com/jberger/Physics-Photoemission}.
Once I am sufficiently confident in its implementation, and more importantly its voracity, I intend to release it to the CPAN as well, most likely under the name \verb!Physics::Photoemission!.
This module depends on the much larger Perl project PDL (\url{http://pdl.perl.org}), a matrix-oriented numerical library, making it slightly more difficult to install, however the speed and implementational simplicity benefit added by that dependency is marked.

Of particular interest to users of \verb!Physics::UEMColumn!, \verb!Physics::Photoemission! also includes a subclass of \verb!Physics::UEMColumn::Photoemission! which uses this binning model to generate the pulse's $z$ direction initial conditions.

%TODO compare to luiten RF compressed pulse system as example (or might go in results section)

>>>>

A simulation script is composed of creating instances of the classes that represent the column, the pulse, electron-optical elements like magnetic lenses and RF cavities.
These objects act as containers for the information about the physical object that they represent.
Further they manage programmatic tasks related to those objects.
For example, electron-optical element objects manage the Gaussian region-of-influence (\ref{eq:reg_of_influence}) and calculate the force that their fields apply to the pulse.
These objects are managed by a central ``simulation'' class (called \verb!Physics::UEMColumn!) which handles the time evolution of the system.
This arrangement allows for clean, manageable and extensible code.

Many scripts which use \verb!Physics::UEMColumn! were needed to generate data and figures used for the preparation of this thesis.
I have included most of them in the source repository which is available at \url{https://github.com/jberger/Thesis}.
In Appendix \ref{sec:script}, I present the simulation scripts used to create \ref{fig:spacecharge_noacc}, \ref{fig:spacecharge_acc} and \ref{fig:compound}, as examples of this implementation.

Additionally, a development version of the bin model presented in Section \ref{sec:bin_model} is available at \url{https://github.com/jberger/Physics-Photoemission}.
Once I am sufficiently confident in its implementation, and more importantly its voracity, I intend to release it to the CPAN as well, most likely under the name \verb!Physics::Photoemission!.
This module depends on the much larger Perl project PDL (\url{http://pdl.perl.org}), a matrix-oriented numerical library, making it slightly more difficult to install, however the speed and implementational simplicity benefit added by that dependency is marked.
Of particular interest to users of \verb!Physics::UEMColumn!, \verb!Physics::Photoemission! also includes a subclass of \verb!Physics::UEMColumn::Photoemission! which uses this binning model to generate the pulse's $z$ direction initial conditions.
